\documentclass{article}

\usepackage{geometry}
\geometry{
    a4paper,
    left=0.65in,
    top=0.70in,
    right=0.65in,
    bottom=0.70in
}

\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=[rgb]{0.10,0.30,0.60}
}

\usepackage{titlesec}
% ── Uniform section-header size (\large) for every \section ──────
\titleformat{\section}
    {\large\bfseries\scshape}
    {}{0em}{}
    [\vspace{1pt}\titlerule\vspace{2pt}]
\titlespacing{\section}{0pt}{10pt}{4pt}

\usepackage{enumitem}
\setlist[itemize]{
    leftmargin=1.2em,
    topsep=3pt,
    itemsep=2pt,
    parsep=0pt,
    label=\textbullet
}

\usepackage{tabularx}
\usepackage{xcolor}
\definecolor{darkgray}{gray}{0.35}
\definecolor{accentblue}{rgb}{0.10,0.30,0.60}

% ── Header helpers ──────────────────────────────────────────────
\newcommand{\resumename}[1]{%
    {\centering\fontsize{22}{26}\selectfont\bfseries #1\par}%
    \vspace{4pt}%
}

% Contact line kept at the uniform body size (\normalsize)
\newcommand{\resumecontact}[1]{%
    {\centering\normalsize\color{darkgray}#1\par}%
    \vspace{6pt}%
}

% ── Job entry helpers ────────────────────────────────────────────
% \job{Company}{Title}{Date}  — all text at uniform body size
\newcommand{\job}[3]{%
    \vspace{6pt}%
    {\textbf{#1} \hfill \textit{#3}}\\[1pt]%
    {\textit{#2}}\par%
    \vspace{2pt}%
}

% \role{Role title}{Date}  — sub-role within same company
\newcommand{\role}[2]{%
    \vspace{4pt}%
    {\textit{#1} \hfill \textit{#2}}\par%
    \vspace{1pt}%
}

\pagestyle{empty}
\setlength{\parindent}{0pt}

% ════════════════════════════════════════════════════════════════
\begin{document}
% ════════════════════════════════════════════════════════════════

\resumename{Rama Krishna G V}

\resumecontact{%
    \href{mailto:gvsriramakrishna@gmail.com}{gvsriramakrishna@gmail.com}
    \enspace\textbar\enspace
    +91 96421 02244
    \enspace\textbar\enspace
    \href{https://linkedin.com/in/ramakrishnagonella}{linkedin.com/in/ramakrishnagonella}
}

%\hrule height 0.8pt
%\vspace{6pt}

% ── Summary ─────────────────────────────────────────────────────
\section{Summary}

Strategic Product Management leader with 17+ years of progressive experience envisioning, building, and scaling B2B and B2C products and platforms. Proven track record of driving multi-million dollar revenue growth, leading cross-functional teams, and delivering AI-powered experiences across enterprise software, SaaS, and productivity platforms. Adept at translating C-level vision into actionable product roadmaps and measurable business outcomes.

% ── Skills ──────────────────────────────────────────────────────
\section{Core Competencies}

\begin{itemize}
    \item \textbf{Product Leadership:} Product Vision \& Strategy, E2E Product Lifecycle Management, Roadmap Development, Go-to-Market Execution, Cross-Functional Leadership, Team Empowerment \& Coaching.
    \item \textbf{Methods \& Practices:} Data-Driven Decision Making, A/B Experimentation, UX Research \& Validation, Telemetry \& Performance Optimization, Market Analysis, Customer Insights.
    \item \textbf{AI \& Platforms:} Microsoft Copilot, ServiceNow AI, Pega Decisioning; Dynamics 365 ERP, ServiceNow CSM, Pega CPQ, Huawei BSS/OSS.
    \item \textbf{Tools \& Engineering:} Cursor, Emergent; C, Java, PL/SQL.
\end{itemize}

% ── Education ───────────────────────────────────────────────────
\section{Education}

\begin{itemize}
    \item \textbf{Post Graduate Diploma in Commerce \& Business} \hfill Jul 2008 -- Oct 2009 \\
          \emph{The University of Auckland Business School, New Zealand}

    \item \textbf{Master of Computer Applications} \hfill May 2003 -- May 2006 \\
          \emph{Jawaharlal Nehru Technological University, India}
\end{itemize}

% ── Certifications ───────────────────────────────────────────────
\section{Certifications}

\begin{itemize}
    \item TOGAF 9.1 Certified Enterprise Architect \textcolor{darkgray}{(License: 125004)}
    \item Pega Certified Business Architect \& Decisioning Architect
\end{itemize}

% ── Career ──────────────────────────────────────────────────────
\section{Career}

% ── Phenom ──
\job{Phenom}{Principal Product Manager — Talent Intelligence Platform}{May 2026 -- Present}
\begin{itemize}
    \item Leading the India PM team responsible for Recruiter and Candidate Experience product areas within the Phenom Talent Intelligence Platform, driving product strategy, vision, and end-to-end execution.
\end{itemize}

% ── Microsoft ──
\job{Microsoft}{Senior Product Manager}{Jan 2020 -- Aug 2025}

\role{Dynamics 365 Project Operations ERP}{}
\begin{itemize}
    \item Defined and executed the AI agentic workflow strategy for Dynamics 365 Project Operations, embedding Human-in-the-Loop (HITL) design patterns that improved task completion rates and user trust while meeting defined KPI benchmarks.

    \item Drove a multi-year strategic roadmap by leveraging C-level executive relationships, establishing cross-product alignment, and partnering with Sales, Marketing, and Customer Success teams to prioritize high-impact capabilities.

    \item Improved core product fundamentals across customer experience, platform performance, and API integrations, contributing to an 11\% improvement in customer retention.
\end{itemize}

\role{Microsoft Office Product Group — Web \& Mobile Platforms}{}
\begin{itemize}
    \item Identified and delivered high-priority Excel capabilities — including contextual help, intelligent search, and inline smart recommendations — directly addressing top customer pain points and contributing \$25M to overall M365 subscription growth.

    \item Conceived and shipped Copilot-powered functions (Create, Analyze, Update, Insert) in Excel for Web and Mobile, serving both B2B and B2C segments and generating \$1.5M in incremental Copilot revenue.

    \item Boosted user-perceived performance of Excel on Web by 60\% through targeted improvements in app startup (async loading, lazy initialization), rendering (prefetch strategies), and interactivity (Time to Interactive, First Contentful Paint), resulting in NPS +1, CSAT +1.5, and a 13\% reduction in churn.

    \item Envisioned and delivered a platform-wide enterprise data protection and governance capability across the M365 suite, generating an \$18M recurring annual revenue stream — achieved through deep collaboration with Microsoft Azure AI, legal, and marketing stakeholders across multiple product organizations.
\end{itemize}

% ── ServiceNow ──
\job{ServiceNow}{Manager, Product Management}{Apr 2019 -- Jan 2020}
\begin{itemize}
    \item Established and scaled the first India-based Go-to-Market (GTM) product team at the IDC for the Customer Service Management (CSM) product line, leading pre-sales engagement, sales enablement, and customer research programs.

    \item Led the team in building best-in-class CSM solution assets and reference architectures that directly supported the closure of enterprise deals worth \$50M within a single fiscal year.
\end{itemize}

% ── Pega ──
\job{Pegasystems}{Associate Business Process Architect}{Sept 2014 -- Mar 2019}
\begin{itemize}
    \item Launched reusable enterprise frameworks for customer acquisition, retention, and cross-sell on the Pega Decisioning platform, reducing product conceptualization-to-market time by 50\% for enterprise clients.

    \item Designed and implemented foundational analytical models on Pega CDH — including Customer Lifetime Value (CLV), Investment Budget allocation, Churn Prediction, and Retention Propensity — empowering enterprises to build profitable product portfolios and accurately forecast revenue growth.

    \item Created end-to-end customer journey templates for acquisition, retention, and cross-sell scenarios, cutting enterprise go-to-market time by 50\% for new product and service launches.
\end{itemize}

% ── Huawei ──
\job{Huawei Technologies R\&D}{Technology Lead}{Mar 2011 -- Sept 2014}
\begin{itemize}
    \item Architected and delivered core features across CRM, Billing, and Activation systems supporting MACD order flows (Move, Add, Change, Disconnect), Lead-to-Cash, Order-to-Activate, and Campaign Management for Tier-1 telecom operators.

    \item Served as a trusted BSS/OSS advisory expert for Telcos across EMEA and APAC regions, guiding solution design for Sales, Support, and Service Management customer journeys.

    \item Played a pivotal role in winning \$30M+ in new business by contributing to RFP responses, solution architecture design, and business process optimization during competitive pre-sales engagements.
\end{itemize}

% ── Auckland ──
\job{University of Auckland}{Research Associate}{Feb 2010 -- Dec 2010}
\begin{itemize}
    \item Delivered undergraduate instruction in Operating Systems, Database Management Systems (DBMS), and C programming as part of an academic research engagement.
\end{itemize}

% ── Convergys ──
\job{Convergys (Information Management Group)}{Systems Analyst}{Jun 2006 -- Jul 2008}
\begin{itemize}
    \item Developed a hybrid customer management module in C and Pro*C, enabling real-time rating and charging on the Infinys Billing platform and the Nokia Charge@Once real-time rating engine.

    \item Managed end-to-end system configuration for rate and bill plans, discount structures, product catalogs, bill formatters, and General Ledger (GL) code integrations.

    \item Built custom bill data formatters using Perl, along with file readers and processors using Pro*C, PL/SQL, and Oracle Advanced Queues.
\end{itemize}

\vspace{10pt}
\begin{center}
    \textcolor{darkgray}{$\cdot\ \cdot\ \cdot\ \cdot\ \cdot$}
\end{center}

\end{document}
